A smart Meter capable of load disaggregation should be tested with a large number of appliances. It is not practical to use actual load to design such meter because it is expensive in terms of time, cost and space. As high voltage is involved, a lot of precautions should be taken while conduction such tests. To speed up this task we developed a voltage and current signal simulator. This simulator enables us to work with low voltage circuits only and test out a large number of appliance combinations without running the actual appliance. This simulator can replay the appliance behavior by using high-speed DAC (digital to analog converter).  As the power measurement requires both voltage and current sensing, two ADC are used to generate these signals.

We have used the NUCLEO-F303RE \cite{NUCLEOF303RESTM32Nucleo64} development board to make this simulator.
The microcontroller on this board has DMA to transfer data from the waveform buffer to the 2 DAC to create smooth analog signals. DMA is used to feed data in both the DAC channels simultaneously. In order to use second the DAC on the nucleus board, the 0-ohm resistor connected to the pin 13 led should be removed, thereby disabling the led.

By taking only a few data samples from an actual appliance or using open data samples like PLAID \cite{gaoPLAIDPublicDataset2014}, we can simulate a large number of appliances in a variety of modes without even procuring the actual appliances. The simulator can also generate different frequency and voltage level data from a single sample collected from the actual appliance.
