For the realization of the smart grid, a large number of smart meters will be installed. The smart meters may become one with the highest penetrated smart devices of the different type of devices in the world because every household which uses electricity will have them. In the future, smart meters should be taking the role of being more than just the measurements devices. They may have a lot of features we cannot imagine now. A lot of research is needed to develop such a smart meter. We have presented a smart meter design that can act as a platform for future smart meter research. The presented smart meter design can be used for large scale deployment. It is an attempt towards making a device that can support not only the present smart grid but can easily support future needs.

Our smart meter is capable of providing high-frequency voltage, current and power data to perform energy disaggregation. This capability will enable the development of smart meters that can perform energy disaggregation without the help of any external processing resources. With such capabilities, it will be easy to enjoy a large acceptance by the end users.

It can support data communication initiated by the meter which drastically reduces the communication bandwidth requirement. This feature will reduce the overhead cost of large scale deployment of the smart meter. The presented meter is cost effective and can be assembled with ease as it uses the most easily available components. This will enable affordable large-scale deployment of smart meters.
