The effect of the room heater and the air conditioners can be observed by installing temperature sensors. Outside temperature can be used identified if the room is being cooled. When the air conditioner is cooling the temperature in the vicinity of the air blower will decrease gradually. It requires some interpretation but a temperature sensor can very accurately identify the state of the air conditioner. But it is not easy to identify the stare of all heating appliances. It is difficult to measure the temperature change for appliances like the water heater or cooking appliance or some cooling appliance like chiller or freezer because they provide thermal isolatin. Temperature measurement will fail to provide an accurate state for such an appliance.

In many cases, the man component of the appliance is a motor which converts the electrical energy to some mechanical form. The compressor of the refrigerator or rotor of a washing machine. These motors generate vibration that can be sensed by sensors to detect the appliance operation.

A number of appliances like a fan and air conditioners circulate the air by means of air flow. For such appliances, the wind speed can be measured to detect if the appliance is on or off. Installing flow sensor is difficult and requires expertise. These sensors are large in size and contain moving parts that make their installation difficult. Because of these reasons flow sensors are used only where no other sensor can be installed. If there is any possibility of measuring other parameters to derive the same information using alternate sensors like temperature, vibration, sound or any other sensor the alternate sensors are generally used.

