Assuming that the power consumed by the appliance is constant and once it is known, only identifying the state of the appliance is sufficient to compute the total power consumed by the appliance during a period.

All electric appliances are to perform some task which in turn causes some physical change on the surroundings. These are all observable changes like light, heat, motion etc. Which is the expected work of the appliance? There could also be some unintended side effects which also affect the surrounding like noise caused by the fan, vibration caused by the compressor of the refrigerator.

\begin{itemize}
    \item Lighting appliance produces enough light to identify it states. Cheap light intensity sensors are available which can be used to identify the lighting appliance state but the accurate placement of such a sensor is very critical because these sensors can easily be misled by daylight or light from nearby lighting equipment.
    \item A sensor like an infrared emitter pair could be used to detect if a fan is moving out stationary or even to measure the speed of the fan. These sensors are impacted by other infrared light sources like the daylight but can be compensated for such different environment. A skilled worker is required to install such a sensor as these sensors should be placed accurately and may be required to calibrated during installation.
    \item Fan and many other appliances like mixer, grinder, or washing machine generate significantly audible noise.  This audio noise can be sanded to detect the appliance state. This is a less reliable sensor because it will sense the noise coming from all directions, and all loud sounds will be detected as noise. In countries like India where high audio noise from vehicles and celebrations is very common, this sensor will generate a large number of false-positive events.
    \item The effect of the room heater and the air conditioners can be observed by installing temperature sensors. Outside temperature can be used identified if the room is being cooled. When the air conditioner is cooling the temperature in the vicinity of the air blower will decrease gradually. It requires some interpretation but a temperature sensor can very accurately identify the state of the air conditioner. But it is not easy to identify the stare of all heating appliances. It is difficult to measure the temperature change for appliances like the water heater or cooking appliance or some cooling appliance like chiller or freezer because they provide thermal isolatin. Temperature measurement will fail to provide an accurate state for such an appliance.
    \item In many cases, the man component of the appliance is a motor which converts the electrical energy to some mechanical form. The compressor of the refrigerator or rotor of a washing machine. These motors generate vibration that can be sensed by sensors to detect the appliance operation.
    \item A number of appliances like a fan and air conditioners circulate the air by means of air flow. For such appliances, the wind speed can be measured to detect if the appliance is on or off. Installing flow sensor is difficult and requires expertise. These sensors are large in size and contain moving parts that make their installation difficult. Because of these reasons flow sensors are used only where no other sensor can be installed. If there is any possibility of measuring other parameters to derive the same information using alternate sensors like temperature, vibration, sound or any other sensor the alternate sensors are generally used.
\end{itemize}

