%Conventionally only resistive, inductive and capacitive loads existed. In an alternating supply, the current drawn by the load is also alternating. for a resistive load, the phase of the sinusoidal alternating current is the same as the phase of the supply voltage.  The voltage and current waveform for the resistive types of load is shown in figure [].

%The power drawn by the load is the product of the voltage and current. In the figure [], voltage and the current waveforms are represented by V and I and the power for the resistive load is given by the curve $Power$. It can be observed that power is positive even when the voltage is negative because the sign of the current is always the same as that of the voltage.

In the case of the inductive load, the power is sometimes negative, which indicates outflow of the power from the inductor, when the sign of the current is not the same as the sign of the voltage. In case of a purely inductive load, the sum of the inflow and the outflow of the power is zero. The amount of power absorbed by the inductor is pushed back into the supply in other parts of the cycle.

The ratio of the power consumed by the appliance to the total power flowing through the wire is known as the power factor. The power not consumed by the appliance and pushed back is known as reactive power. Electrical meters can measure reactive power and power factor also.

In reality, most appliance, like electric motors which have inductors or coils consist of some resistive and some inductive component. Hart used both active and reactive power measured at the mains to identify the appliance state. So both the nature of the appliance and the power rating of the appliance are used to identify the appliance.

% for a capacitive load, the current wave leads ahead of the voltage while for an inductive load the current wave lags behind the voltage.

Unfortunately, this approach works only when one of each type of appliance is installed in a house.  It also fails when more than one electrically similar type of appliances are installed in the house like a fan and a motor.
