In this analysis, current sensors were used at all the places except for the mains meter. The simulation results show that the number of the current sensors required is identical to the requirement of the smart meters. This is because the power measured by the smart meter is mostly dependent on the current drawn by the appliance. The current sensor may perform poorly only in the case when more than one appliance draws the same current, but have different active and reactive power. In our simulations, we have not used appliances of this nature. Because of this property, a large number of products use them instead of smart meter thereby reducing the complexity of the sensor and the cost of the sensor itself. This also reduces the installation complexity if the clamp-on type of sensor is used.

The key point to be noted that the current sensor can never outperform the number of smart meter requirement.
that is $$O_W \le O_C$$

Prior to this work, the voltage sensed by the smart meter is not used for any purpose at all. Based on the technique proposed by us, the voltage sensed by the smart meter can be used to identify the state of the nearby appliances. When smart meters are installed at locations where the voltage sensed by the meter can be utilized to identify the appliance state the number of meters requirement can be reduced.

Figure \ref{fig:sensreq} shows that the number of smart meters required grows proportional to the number of appliances, but the rate of increase is lower when compared when smart meters are used for the power measurement only. The reduction in the number of smart meters is higher in this case and can be up to 30-40\% for $type 1$ layouts. For the moderately diverse appliances ( $type 2$ layouts), the number of smart meter requirement can be reduced by 60\% to that of the total number of appliance installed.  This can be observed in the results shown in figure \ref{fig:sensreq}. As the inference made by the  voltage can only reduce the number of the smart meters, the relative number of sensors required will be less than the number of meters required $$O_P \le  O_W \le  O_C$$
